Lesson 5
========================================================

```{r}
setwd('~/workspace/analytics_treinamento_R/explore_many_variables')
getwd()
library(ggplot2)
library(dplyr)
pf <- read.csv('~/workspace/analytics_treinamento_R/explore_two_variables/pseudo_facebook.tsv', sep = '\t')
```

### Multivariate Data
Notes: vamos aprender a analisar três ou mais variáveis.

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.t = mean, geom = 'point', shape = 4)
```

```{r}
pf.fc_by_age_gender <- subset(pf, !is.na(gender)) %>%
    group_by(age, gender) %>%
    summarise(mean_friend_count = mean(friend_count), 
        median_friend_count = median(friend_count), 
        n = n()) %>%
    ungroup() %>%
    arrange(age)
```


***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = median_friend_count), data = pf.fc_by_age_gender) +
  geom_line(aes(color = gender))
```

***

### Thinking in Ratios
Notes: POdemos pensar em quantas vezes usuários female tem em média a mais que os usuários male.

***

### Wide and Long Format
Notes: As vezes é preciso modificar a forma como os dados estão organizados para uma melhor análise.

***

### Reshaping Data
Notes:

```{r}
#install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender, 
                                  value.var = 'median_friend_count')
```

Outra maneira
```{r}
library(tidyr)
pf.fc_by_age_gender.wide <- subset(pf.fc_by_age_gender[c('age', 'gender', 'median_friend_count')]) %>%
  spread(gender, median_friend_count) %>%
  mutate(ratio = female / male)
```

***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x = age, y = ratio), data = pf.fc_by_age_gender.wide) +
  geom_line() +
  geom_hline(yintercept = 1, color = I('red'), linetype = 2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - (pf$tenure / 365))
```

***

### Cut a Variable
Notes: Categorizar a variável ano em faixas, para uma melhor visualização.

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined, breaks=c(2004,2009,2011,2012,2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(aes(x = age, y = friend_count),  data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count),  data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 5)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, tenure >0), summary(friend_count / tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.2205
What is the maximum friend rate?
417

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure), 
       data = subset(pf, pf$tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

```{r}
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))
```



***

### Sean's NFL Fan Sentiment Study
Notes: O trabalho de Sean foi analisar os altos e baixos nos posts dos fãs, antes, durante e após um começo de um jogo da NFL, e como esses posts se comportam quando o time
do qual se é fã perde ou ganha.

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes: O preço acima de 60 é bem acima dos demais se aumentarmos o binwidth. Alterando a visualização inicial que mostra que os preços de forma discreta.

```{r Histograms Revisited}
yo <- read.csv('yogurt.csv')
str(yo)

yo$id <- factor(yo$id)
str(yo)
```
```{r}
ggplot(aes(x = price), data = yo) +
  geom_histogram(fill = I("#099DD9"))

ggplot(aes(price), data=yo) + geom_histogram(binwidth=10, fill=I("#099DD9"))

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
summary(yo)

length(unique(yo$price))
table(yo$price)
```

```{r}
yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)
```


***

### Prices over Time
Notes: Os preços mais comuns(acima de 60), tendem a aumentar com o tempo.

```{r Prices over Time}
ggplot(aes(x = all.purchases), data = yo) +
  geom_histogram(binwidth = 1)
```

```{r}
ggplot(aes(x = time, y = price), data = yo) +
  geom_jitter(alpha = 0.20)
```


***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

